---
title: "Reproducible Research: Peer Assessment 1"
output: 
  html_document:
    keep_md: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


## Loading and preprocessing the data

```{r import}
dataset = read.csv('./activity.csv')
dataset2 = dataset[!is.na(dataset$steps), ]
head(dataset2)
```


## What is mean total number of steps taken per day

```{r statistics, fig.height=4}
sum.step = with(dataset2, tapply(steps, date, sum))
hist(sum.step, main="total steps per day", xlab='Steps')

mean.step = format( mean(sum.step, na.rm=TRUE), nsmall=2)
med.step  = median(sum.step, na.rm=TRUE)
```

Mean steps taken per day is `r mean.step`. Median steps taken per day is `r med.step`.


## What is the average daily activity pattern?

```{r dailyactivity, fig.height=4}
ave.step = with(dataset2, tapply(steps, interval, mean))
plot(names(ave.step), ave.step, type="l", lwd=2, las=1,
     xlab = 'Interval', ylab = 'Average steps',  main='Daily activity')
max.interval = names(which.max(ave.step))
```

Among all the 5-minutes intervals, the interval which contains the maximum average steps was `r max.interval`. 


## Imputing missing values
```{r missingvalue}
na.num <- sum(is.na(dataset$steps))

dataset3 = dataset
dataset3$steps[is.na(dataset3$steps)] = mean(dataset2$steps)

sum.step2 = with(dataset3, tapply(steps, date, sum))
hist(sum.step2, main="total steps per day", xlab = 'Steps')

mean.step2 = format( mean(sum.step2), nsmall=2)
med.step2  = format( median(sum.step2, nsmall=2) )
```
The number of missing value in dataset was `r na.num`.   

After imputing missing data, mean steps taken per day became `r mean.step2`, and median steps taken per day became `r med.step2`.   

The mean and mediam were not affected so much but the shape of histgram became sharper distribution than previous histgram as the missing values were replaced with average of total taily numper of steps.   


## Are there differences in activity patterns between weekdays and weekends?

```{r compare.days, message=FALSE}
library(dplyr)
library(ggplot2)

dataset3$days = factor(1*(weekdays(as.Date(dataset3$date)) %in% c('Sunday', 'Saturday')),
                       label=c('weekday', 'weekend'))

ds <- dataset3 %>%
        group_by(days, interval) %>%
            summarise( step.mean = mean(steps)) 

ggplot(ds, aes(interval, step.mean)) + geom_line() + facet_grid(days~.)

```